Maragra-CISM status report

### 2017-08-21 analyses/analyze_monthly_data.Rmd
major structuring

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(brew)
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

@@

```{r}
# Packages
library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(ggthemes)
library(RColorBrewer)
library(pander)

# Read data
df <- read_csv(file = 'data/maragra_monthly_data.csv')

# Create date column
df$date <- as.Date(paste0(df$year, '-', df$month, '-', 15))

# Create a percent postiive column
df$percent_positive <- df$positive / df$tested * 100

# Arrange by date
df <- df %>% arrange(date)

# Get rid of any unknowns
df <- df %>% filter(!is.na(tested))
```

@@

```{r}
x <- 
  df %>%
  group_by(date) %>%
  summarise(p = sum(positive),
            pp = sum(positive) / sum(tested) * 100,
            tested = sum(tested))

@@

```{r, results = 'asis'}
gg <- gvisLineChart(data = df %>% filter(group == 'nacionais'),
                    xvar = 'date',
                    yvar = c('tested', 'positive'),
                    options = list(curveType='function',
                                  title="Malaria among Mozambican employees",
                                  titleTextStyle="{color:'black',fontName:'Courier',fontSize:16}"))
plot(gg)

gg <- gvisLineChart(data = df %>% filter(group == 'expatriados'),
                    xvar = 'date',
                    yvar = c('tested', 'positive'),
                    options = list(curveType='function',
                                  title="Malaria among expatriated employees",
                                  titleTextStyle="{color:'black',fontName:'Courier',fontSize:16}"))
plot(gg)
# 
# # Heat calendar chart
# gvisCalendar

# # # Motion chart
# x <- gvisMotionChart(df,
#    idvar="group",
#    timevar="date")
```

@@

```{r}
ggplot(data = y,
       aes(x = date,
           y = val,
           group = key,
           fill = key)) +
  geom_area(stat = 'identity', position = 'stack', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_wsj() +
  scale_fill_manual(name = '',
                    values = c('darkgreen', 'darkred')) +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, absolute') +
    theme(title = element_text(size = 12))

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = pp)) +
  geom_area(stat = 'identity', fill = 'darkblue', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_wsj() +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, relative') +
    theme(title = element_text(size = 12))

@@

```{r}
make_month_name <- function(number){
  format(as.Date(paste0('2015-', number, '-01')), '%B')
}
x <- df %>%
  # mutate(day_number = as.numeric(format(date, '%j'))) %>%
  # mutate(day_number = round(day_number, -1) + 5)
  mutate(month_number = as.numeric(format(date, '%m'))) %>%
  group_by(month_number, year) %>%
  summarise(p = sum(positive),
            pp = sum(positive) / sum(tested) * 100) %>%
  mutate(year = factor(year,
                       levels = as.character(2011:2016))) %>%
  ungroup %>%
  mutate(month_number = factor(make_month_name(month_number),
                               levels = make_month_name(1:12)))

@@

```{r}
df %>%
  dplyr::select(year, month, group, tested, positive, negative) %>%
  pander
```

>>>>

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(brew)
library(maragra)
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

@@

```{r}
# Packages
library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(ggthemes)
library(RColorBrewer)
library(pander)
library(cism)

# Read data
clinic_agg <- maragra::clinic_agg

# Create date column
clinic_agg$date <- as.Date(paste0(clinic_agg$year, '-', clinic_agg$month, '-', 15))

# Create a percent postiive column
clinic_agg$percent_positive <- clinic_agg$positive / clinic_agg$tested * 100

# Arrange by date
clinic_agg <- clinic_agg %>% arrange(date)

# Get rid of any unknowns
clinic_agg <- clinic_agg %>% filter(!is.na(tested))
```

@@

```{r}
x <- 
  clinic_agg %>%
  group_by(date) %>%
  summarise(p = sum(positive),
            pp = sum(positive) / sum(tested) * 100,
            tested = sum(tested))

@@

```{r, results = 'asis'}
gg <- gvisLineChart(data = clinic_agg %>% filter(group == 'nacionais'),
                    xvar = 'date',
                    yvar = c('tested', 'positive'),
                    options = list(curveType='function',
                                  title="Malaria among Mozambican employees",
                                  titleTextStyle="{color:'black',fontName:'Courier',fontSize:16}"))
plot(gg)

gg <- gvisLineChart(data = clinic_agg %>% filter(group == 'expatriados'),
                    xvar = 'date',
                    yvar = c('tested', 'positive'),
                    options = list(curveType='function',
                                  title="Malaria among expatriated employees",
                                  titleTextStyle="{color:'black',fontName:'Courier',fontSize:16}"))
plot(gg)
# 
# # Heat calendar chart
# gvisCalendar

# # # Motion chart
# x <- gvisMotionChart(clinic_agg,
#    idvar="group",
#    timevar="date")
```

@@

```{r}
ggplot(data = y,
       aes(x = date,
           y = val,
           group = key,
           fill = key)) +
  geom_area(stat = 'identity', position = 'stack', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_cism() +
  scale_fill_manual(name = '',
                    values = c('darkgreen', 'darkred')) +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, absolute') +
    theme(title = element_text(size = 12))

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = pp)) +
  geom_area(stat = 'identity', fill = 'darkblue', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_cism() +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, relative') +
    theme(title = element_text(size = 12))

@@

```{r}
make_month_name <- function(number){
  format(as.Date(paste0('2015-', number, '-01')), '%B')
}
x <- clinic_agg %>%
  # mutate(day_number = as.numeric(format(date, '%j'))) %>%
  # mutate(day_number = round(day_number, -1) + 5)
  mutate(month_number = as.numeric(format(date, '%m'))) %>%
  group_by(month_number, year) %>%
  summarise(p = sum(positive),
            pp = sum(positive) / sum(tested) * 100) %>%
  mutate(year = factor(year,
                       levels = as.character(2011:2016))) %>%
  ungroup %>%
  mutate(month_number = factor(make_month_name(month_number),
                               levels = make_month_name(1:12)))

@@

```{r}
clinic_agg %>%
  dplyr::select(year, month, group, tested, positive, negative) %>%
  kable
```
